An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-21 paper/4.xpg.tex
merged

@@

\textcolor{red}{
In $kpg$, basically, functions for the updates are kept (but not evaluated) in $lks$ and $lkv$.
In $\kpginline{RearrS}$ and $\kpginline{RearrV}$, $f_1$ and $g_1$ are accumulated in $lks$ and $lkv$.
These two functions are evaluated in $\kpginline{Skip}$ and $\kpginline{Case}$ by applications of $lks \ s$ and $lkv \ v$. At the same time, the third arguments and fourth arguments of recursive calls are updated with the identity functions.
This evaluation is needed, because these definitions require the actual values, $es$ and $ev$.
Thanks to this update, accumulation in $kpg$, $\underline{lks_1}$ and $\underline{s_1}$ in $\kpginline{bx_1 \circ bx_2}$ are not evaluated as much as possible.}
%Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$.}

>>>>

    %{\textcolor{red}{BX programs that have an efficient inverse evaluation are not affected by this restriction, but not all BX programs have this property. An example restricted by this is evaluating $bsnoc$ with different length of a source and a view.}}

@@

\textcolor{red}{
In $kpg$, basically, functions for the updates are kept (but not evaluated) in $lks$ and $lkv$.
In $\kpginline{RearrS}$ and $\kpginline{RearrV}$, $f_1$ and $g_1$ are accumulated in $lks$ and $lkv$.
The kept functions are evaluated in $\kpginline{Skip}$ and $\kpginline{Case}$ by applications of $lks \ s$ and $lkv \ v$. At the same time, the third and fourth argument of recursive calls are updated with the identity function.
This evaluation is needed because these definitions require the actual values, $es$ and $ev$.
Thanks to this update, accumulation in $kpg$, $\underline{lks_1}$ and $\underline{s_1}$ in $\kpginline{bx_1 \circ bx_2}$ are not evaluated as much as possible.}
%Except $\kpginline{Skip}$ and $\kpginline{Case}$ where $s$ and $v$ hold actual values, functions for the computation will be kept in $ks'$ and $kv'$.}
